---
title: "Bush 631: Class Task 3"
output:
  pdf_document: default
author: Your Name
date: "`r Sys.Date()`"
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

# Upload any required package in this chunk
library(readxl)
library(tidyverse)
library(haven)

# Upload data
insurgentdata <- read_dta("~/Dropbox/TAMU/Bush631_QuantMethods/Week3_Causality_II/Data_ClassTask1.dta")

```

## Making plots in R Markdown
In this task we learn how to make plots

### Insurgent data
Using the class tasks data - Insurgent groups (1998-2012).  

* Definition in code chunks:  

  - echo = TRUE for displaying code on PDF.
  - warning = FALSE to not display warnings from code with output.
  - message = FALSE to not display messages with output.
  - include = TRUE to include output like data analysis and plots.

\vspace{2em}

```{r, echo=TRUE, include=TRUE}

# Add R code here
x <- c(1,2,3,4)
x

y <- sum(x)
y
```
\vspace{1em}

* For plots:  

  - out.width = enter (in percentages) how much the plots covers from the page (I usually use 80-90%).
  - fig.align = center will place the plot at the center of the screen. 
  
* Task requirements:  

  1. Plot the distribution of GDP/cap variable.
  2. Plot the variables: Civilian fatalities vs. police and military fatalities

\vspace{1em}
```{r, echo=TRUE, include=TRUE, warning=FALSE, message=FALSE, fig.align='center', out.width="85%"}

# Plot 1: GDP/cap - using tidyverse
ggplot(insurgentdata, aes(x=gle_rgdpc)) +
  geom_histogram() + theme_bw()

```
\vspace{1em}

```{r, echo=TRUE, include=TRUE, warning=FALSE, message=FALSE, fig.align='center', out.width="85%"}

# Plot 2: Civilian fatalities vs. police and military fatalities - using tidyverse
ggplot(insurgentdata, aes(x=rev_nonpm_fatalities,y=rev_pm_fatalities)) +
  geom_point() + theme_bw()

```



